### 2017-08-25 paper/CoverLetter.tex
Courried package name

In this application manuscript entitled ``dispRity: an R package for measuring disparity'', I present a complete and flexible R package for running multidimensional analysis where each parameter can be easily defined by the user (the space, the metric and the test).
This package provides a tidy and modular environment where users can use their own multidimensional space defined as a matrix and apply to it any metric and any test (provided as functions).
This allows for highly modular multidimensional analysis and the tidy interface allows easily reproducible analysis.
All functions have documentation and unit tests. 
Additionally, this package comes with an in depth Gitbook manual covering most functionalities that will be updated regularly following user requests. 
Finally, the package is likely to be well cited as it is already being used in at least five projects that I am aware of.

>>>>

In this application manuscript entitled ``\texttt{dispRity}: an R package for measuring disparity'', I present a complete and flexible R package for running multidimensional analysis where each parameter can be easily defined by the user (the space, the metric and the test).
This package provides a tidy and modular environment where users can use their own multidimensional space defined as a matrix and apply to it any metric and any test (provided as functions).
This allows for highly modular multidimensional analysis and the tidy interface allows easily reproducible analysis.
All functions have documentation and unit tests. 
Additionally, this package comes with an in depth Gitbook manual covering most functionalities that will be updated regularly following user requests. 
Finally, the package is likely to be well cited as it is already being used in at least five projects that I am aware of.
